### 2018-05-29 draft.Rmd
draft 2

---
bibliography: bibliography.bib
editor_options:
  chunk_output_type: console
output:
  html_document:
    df_print: paged
  word_document:
    df_print: kable
    fig_caption: yes
    reference_docx: reference.docx
---

>>>>

---
bibliography: bibliography.bib
editor_options:
  chunk_output_type: console
output:
  word_document:
    df_print: kable
    fig_caption: yes
    reference_docx: reference.docx
  html_document:
    df_print: paged
---
